A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-26 manuscript.Rmd
merge sections on data checking and synthetic creation

## Data Integrity (optional)

@@

We did the same for our simulation to verify that the simulation is really reproducible[^simhash].

@@

## Anonymising Data (optional)

<!-- Should we add a section on synthetic data generation? -->
<!-- Hands on: Create synthetic data -->

>>>>

## If you can not make the data public (optional)

@@

We employed the same mechanism for our simulation to verify that the simulation is really reproducible[^simhash].

@@

An compromise between making the data publicly available and keeping it closed is to publish synthetic data.
Such approach tries to recreate the marginal distribution and bivariate relationships in simulated data, e.g. with the R package `synthpop`[@nowokSynthpopBespokeCreation2016].
The results of such data should generally not be interpreted.
However, synthetic data provides an opportunity for researcher to test if a project is in principle reproducible, even though they have no access to the data.
